Fixing Vulnerabilities Hinders Maintainability

### 2019-01-30 paper/ICPC19/icpc19.tex
more info

\noindent
In this paper, we present the results of our analysis on the maintainability of
607 security changes collected from open-source software.

>>>>

\noindent
In this paper, we present the results of our analysis on the maintainability of
607 security changes collected from open-source software, from different
programming languages.
